### 2011-05-05 paper/paper.tex
removed code from implementation details, but added details about our regions.

@@

Here is the code for the separation oracles which define the cube, the sphere, and the simplex:

\begin{quote}
\begin{verbatim}
bool cube_separation_oracle(point p) {
    for(int i = 0; i<p.n; i++) {
        if(p.x[i] <= -1 || p.x[i] >= 1) return false;
    }
    return true;
}

bool sphere_separation_oracle(point p) {
    real square_norm = 0.0;
    for(int i = 0; i<p.n; i++) {
        square_norm += p.x[i] * p.x[i];
    }
    return square_norm < 1.0;
}

bool simplex_separation_oracle(point p) {
    real c = (1.0 - sqrt(1.0 + (real)p.n)) / (real)p.n;
    real coordsum = 0.0;
    for(int i = 0; i < p.n; i++) {
         coordsum += p.x[i];
    }
    real lambda = (1.0 - (real)p.n * c) / (coordsum - (real)p.n * c);
    if(lambda < 1.0)
        return false;
    for(int i = 0; i < p.n; i++) {
        if(c + lambda * (p.x[i] - c) < 0.0f)
            return false;
    }
    return true;
}
\end{verbatim}
\end{quote}

>>>>

\subsection{The regions}

We implemented separation oracles for a cube, a sphere, and a simplex for dimensions and tested the algorithms for dimensions $n\in\{2,3,4,7,10,100\}$.
\begin{itemize}
\item \emph{The cube.} This is simply the region $(-1,1)^n$.
\item \emph{The sphere.} This is simply the region $\{(x_1,...,x_n)\in\mathbb{R}^n : x_1^2 + x_2^2 + \cdots + x_n^2 < 1\}$.
\item \emph{The simplex.} We defined this as the region inside the convex hull of the points $e_1, ..., e_n$ (defined by $e_{i,j} = 1$ if $i=j$ and $e_{i,j} = 0$ otherwise) and $f = (c,c,...,c)$ where\linebreak $c = (1 - \sqrt{n + 1}) / n$. We can compute that any two of these $n+1$ points are of Euclidean distance $\sqrt{2}$ from each other. To test if a point $p$ lies inside the simplex, we draw a line through $f$ and $p$, and intersect it with the plane $x_1 + x_2 + \cdots + x_n = 1$, say this intersection is $q$. First, we want to check that $p$ lies between $f$ and $q$. If so, then we just need to check that $q$ lies in the convex hull of $e_1,e_2,...,e_n$, but this is equivalent to checking that each coordinate of $q$ is nonnegative.
\end{itemize}

\subsection{Randomness}

@@
